---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/rpdo.svg?branch=master)](https://travis-ci.org/poissonconsulting/rpdo)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/rpdo?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/rpdo)
[![Coverage Status](https://img.shields.io/codecov/c/github/poissonconsulting/rpdo/master.svg)](https://codecov.io/github/poissonconsulting/rpdo?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/rpdo)](https://cran.r-project.org/package=rpdo)
[![CRAN Downloads](http://cranlogs.r-pkg.org/badges/grand-total/rpdo)]( https://CRAN.R-project.org/package=rpdo)

# rpdo

## PDO Index

`rpdo` is an R data package of Monthly Pacific Decadal Oscillation (PDO) index 
values from `r month.name[rpdo::pdo$Month[1]]` `r rpdo::pdo$Year[1]` to `r month.name[rpdo::pdo$Month[nrow(rpdo::pdo)]]` `r rpdo::pdo$Year[nrow(rpdo::pdo)]`.

The function `download_pdo()` scrapes the most recent 
data from <http://research.jisao.washington.edu/pdo/PDO.latest>.

```{r, fig.width=5, fig.height=5, warning=FALSE, fig.cap="Pacific Decadal Oscillation (PDO) Index for January by year."}
library(rpdo)
library(ggplot2)

ggplot(data = subset(rpdo::pdo, pdo$Month == 1), aes(x = Year, y = PDO)) + 
geom_smooth(span = 0.1, se = FALSE, color = "black", method = 'loess') + geom_point() + ylab("January PDO Index")
```

## Installation

To install and load the most recent release from CRAN
```
install.packages("rpdo")
library(rpdo)
```

To install and load the development version from GitHub
```
devtools::install_github("rpdo")
library(rpdo)
```

## Information

For more information see <http://research.jisao.washington.edu/pdo/PDO.latest>.
